Study Comparison

### 2025-03-26 analysis/study_comaprison.Rmd
commit remaining files

```{r}
design <- "12
33"
comparison <- saliva_pl + prob_pl + time_pl + plot_layout(design = design, widths = c(11, 5), heights = c(6, 11))
ggsave(plot = comparison, file = "../results/comparison.pdf", width = 16 / cm(1), height = 17 / cm(1))
ggsave(plot = comparison, file = "../results/comparison.png", width = 16 / cm(1), height = 17 / cm(1))
```

>>>>

```{r}
design <- "12
33"
comparison <- saliva_pl + prob_pl + time_pl + plot_layout(design = design, widths = c(11, 5), heights = c(6, 11))
ggsave(plot = comparison, file = "../results/comparison.pdf", width = 16 / cm(1), height = 17 / cm(1))
ggsave(plot = comparison, file = "../results/comparison.png", width = 16 / cm(1), height = 17 / cm(1))
ggsave(plot = comparison, file = "../results/comparison.tiff", width = 16 / cm(1), height = 17 / cm(1))
```
